%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec,textcomp}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{etaremune} % for reverse numbering
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheadingthreelines}[6]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
		\textit{\small#5} & \textit{\small #6} 
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4}
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING----------
	% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
	%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
	% \end{tabular*}
	
	\begin{center}
		\textbf{\Huge \scshape Lili Zheng} \\ \vspace{1pt}
		\begin{center}{\small Homepage: \href{https://Lili-Zheng-stat.github.io}{https://lili-zheng-stat.github.io}\\Email: llzheng@illinois.edu}
	\end{center}
	\end{center}
	\section{Working Experience}
	 \textbf{Postdoctoral researcher}\hfill 2021 -- Now\\
	{\em \small Department of Electrical and Computer Engineering, Rice University}\\
	 {\em \small Advisor: Genevera I. Allen}
	%-----------EDUCATION-----------
	\section{Education}
	\textbf{University of Wisconsin - Madison}\hfill {2016 -- 2021}\\
	{\em{\sl Ph.D.}, Statistics}\\
	{\em \small Advisor: Garvesh Raskutti}\\
	\textbf{University of Science and Technology of China}\hfill {2012 -- 2016}\\
	{\em \small{\sl B.S.}, Statistics}
	%-----------EXPERIENCE-----------
	\section{Research Interest}
	Graphical models, missing data, distribution-free inference, tensor data analysis, network Granger causality, dependent data, high-dimensional statistics, stochastic algorithms, non-convex optimization
	
		\section{Honors}
	{ Gold Medal Young Researcher Poster Competition Award, \\Conference on Recent Advances in Statistics and Data Science at Rutgers. \hfill 2023\\
		
		IMS Hannan Graduate Student Travel Award.\hfill 2021\\
		Travel grant from Institute for Foundations of Data Science (IFDS), UW-Madison.\hfill                       2019\\
		Travel grant from IMA workshop on Forecasting from Complexity.\hfill                              2018\\
		%First place in qualifying exam, UW-Madison.\hfill                                                2017\\
		Honorable Mention in Mathematical Contest of Modeling, COMAP (Top 20\%)\hfill        2015\\
		National scholarship, USTC. (Top 2\%)\hfill                                       2015\\
		%Excellent Student Cadre, USTC(Top 6\%)\hfill                                       2013\\
		Outstanding freshman scholarship, USTC(Top 20\%)\hfill                                   2012\\}
	
	%-----------PROJECTS-----------
	\section{Publications}
	(*: equal contribution)
	\subsection*{Preprints}
	\begin{etaremune}[start=15]
		\item {\bf L. Zheng}$^{*}$, A. Chang$^{*}$, G. I. Allen, ``Cluster Quilting: Spectral Clustering for Patchwork Learning". {\em Submitted}, \href{https://arxiv.org/abs/2406.13833}{https://arxiv.org/abs/2406.13833}.
		\item J. Liu$^{*}$, {\bf L. Zheng}$^{*}$, Z. Zhang, G. I. Allen, ``Joint Semi-Symmetric Tensor PCA for Integrating Multi-modal Populations of Networks". {\em Submitted}, \href{https://arxiv.org/abs/2312.14416}{https://arxiv.org/abs/2312.14416}. 
		\item {\bf L. Zheng}, G. Raskutti, ``High-dimensional Multi-class Classification with Presence-only Data". \href{https://arxiv.org/abs/2304.09305}{https://arxiv.org/abs/2304.09305}.
		\item L. Gan$^{*}$, {\bf L. Zheng}$^{*}$, G. I. Allen ($*$: equal contribution), ``Model-Agnostic Confidence Intervals for Feature Importance: A Fast and Powerful Approach Using Minipatch Ensembles". \href{https://arxiv.org/abs/2206.02088}{https://arxiv.org/abs/2206.02088}.
		\item A. Chang, {\bf L. Zheng}, G. I. Allen, ``Low-Rank Covariance Completion for Graph Quilting with Applications to Functional Connectivity". {\em under revision at Journal of the American Statistical Association, Applications and Case Studies}, \href{https://arxiv.org/abs/2209.08273}{https://arxiv.org/abs/2209.08273}.
	\end{etaremune}
	\subsection*{Peer-reviewed Journal Publications}
	\begin{etaremune}[start=10]
		\item {\bf L. Zheng}, G. I. Allen, ``Graphical Model Inference with Erosely Measured Data", {\em Journal of the American Statistical Association, Theory and Methods}, 2023.
		\item  A. Chang$^{*}$, {\bf L. Zheng}$^{*}$, G. Dasarathy, G. I. Allen,``Nonparanormal Graph Quilting with Applications to Calcium Imaging", {\em STAT}, 2023.
		\item G. I. Allen, L. Gan, {\bf L. Zheng}, ``Interpretable Machine Learning for Discovery: Statistical Challenges \& Opportunities", {\em Annual Review of Statistics and Its Application}, 2023.
		\item H. Chen$^{*}$, {\bf L. Zheng}$^{*}$, R. A. Kontar, G. Raskutti ($*$: equal contribution), ``Gaussian Process Parameter Estimation Using Mini-batch Stochastic Gradient Descent: Convergence Guarantees and Empirical Benefits'', {\em Journal of Machine Learning Research}, 2022.
		\item Y. Zhou, A. R. Zhang, {\bf L. Zheng}, Y. Wang, ``Optimal High-order Tensor SVD via Tensor-train Orthogonal
		Iteration'', {\em  IEEE Transactions on Information Theory}, 2022.
		\item {\bf L. Zheng}, G. Raskutti, R. Willett, B. Mark, ``Context-dependent Networks in Multivariate Time Series: Models, Methods, and Risk Bounds in High Dimensions'', {\em Journal of Machine Learning Research}, 2021.
		\item {\bf L. Zheng}, G. Raskutti, ``Testing for High-dimensional Network Parameters in Auto-regressive Models'', {\em Electronic Journal of Statistics}, 2019.
	\end{etaremune}
	\subsection*{Peer-reviewed Conference Publications}
\begin{etaremune}[start=3]
	\item {\bf L. Zheng}, Z. T. Rewolinski, G. I. Allen, ``A Low-Rank Tensor Completion Approach for Imputing Functional Neuronal Data from Multiple Recordings", {\em IEEE Data Science and Learning Workshop (DSLW)}, 2022.
	\item {\bf L. Zheng}, G. I. Allen, ``Learning Gaussian Graphical Models with Differing Pairwise Sample Sizes", {\em IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}, 2022.
	\item  H. Chen$^{*}$, {\bf L. Zheng}$^{*}$, R. A. Kontar, G. Raskutti ($*$: equal contribution), ``Stochastic Gradient Descent in Correlated Settings: A Study on Gaussian Processes", {\em Neural Information Processing Systems (NeurIPS)}, 2020.
\end{etaremune}
	\section{Software}
	\begin{itemize}
		\item ``tt\_TTOI: Tensor-Train Orthogonal Iteration", contribute python functions to the \verb|Python| library {\bf TensorLy}, 2022.
		%\item ``TTOI: Tensor-Train Orthogonal Iteration", \verb|Matlab| functions, 2020
		\item ``Network inference for autoregressive models", \verb|R| and \verb|Matlab| functions with tutorials, 2020.
	\end{itemize}
	\section{Teaching and Mentoring Experience}
	\subsection*{Teaching}
	The Summer Institute for Statistics in Big Data, Teaching Assistant\hfill Summer 2023\\
	Stat 301 (Introduction to Statistical Methods), Teaching Assistant \hfill Fall 2016/ Spring 2017
	\subsection*{Mentoring}
	\begin{enumerate}
		\item Camille Little, PhD candidate, Electrical and Computer Engineering, Rice University.
		\item Jiaming Liu, PhD candidate, Statistics, Rice University.
		\item Quan Le, former undergraduate student, Computer Science and Mathematics, Rice University, 2023; now a PhD student at Yale.
		\item Zach Rewolinski, former undergraduate student, Statistics and Computer Science, Rice University, 2023; now a PhD student at UC Berkeley.
	\end{enumerate}

	\section{Presentations}
	\begin{itemize}
		\item Invited talk at Cornell University, 2/28/2024
		\item Invited talk at the University of California, San Diego, 2/15/2024
		\item Invited talk at the University of British Columbia, 2/8/2024
		\item Invited talk at the University of Waterloo, 2/5/2024
		\item Invited talk at the University of California, Irvine, 1/30/2024
		\item Invited talk at the University of Illinois at Urbana-Champaign, 1/25/2024
		\item Invited talk at the University of Michigan, 1/19/2024
		\item Invited talk at the University of California, San Diego, 1/12/2024
		\item Invited talk at the University of Florida, 12/6/2023
		\item Contributed talk at Joint Statistical Meetings, 2023
		\item Poster presentation at ``Conference on Recent Advances in Statistics and Data Science," Rutgers University, 2023
		\item Poster presentation at the conference ``Statistical Foundations of Data Science and their Applications," Princeton University, 2023
		\item Talk in a topic-contributed session at Joint Statistical Meetings, 2022
		\item Poster presentation at ``Workshop on Distribution-Free Uncertainty Quantification," ICML, 2022
		\item Talk at IEEE Data Science and Learning Workshop, 2022
		\item Poster presentation at ICASSP, 2022
		\item Poster presentation at the ``Conference on Advances in Bayesian and Frequentist Statistics," Rutgers University, 2022
		\item Poster presentation at the workshop ``Perspectives in Statistical Modeling and Inference," University of Pennsylvania, 2021
		\item Poster presentation at Joint Statistical Meetings, 2020
		\item Poster presentation at NeurIPS, 2020
		\item Poster presentation at Joint Statistical Meetings, 2019 
	\end{itemize}
	\section{Professional Service}
	\begin{itemize}
		\item Organizer for a topic-contributed session in Joint Statistical Meetings, 2022\\
		\item Session chair for ICASSP, 2022\\
		\item Journal referee (17 in total, \# in parenthesis): {\em Journal of the Royal Statistical Society: Series B} (1), {\em Journal of the American Statistical Association} (1), {\em Biometrika} (1), {\em Journal of Machine Learning Research} (8), {\em Annals of Applied Statistics} (2), {\em IEEE Transactions on Information Theory} (2), {\em Journal of Computational and Graphical Statistics} (1), {\em Computational Statistics and Data Analysis} (1)
		\item Conference reviewer: {\em International Conference on Artificial Intelligence and Statistics (AISTATS) 2021}, {\em International Conference on Machine Learning (ICML) 2022}.
	\end{itemize}
	\section{Programming Skills}
	 R language,  MATLAB, Python
\begin{comment}
	\section{References}
\begin{tabular}{lr}
	% Referee 1
	\begin{minipage}[t]{2.5in}
		Prof.\ Genevera I. Allen\\
		Rice University\\
		Location B\\
		Country and Postcode\\
		\Telefon\ +00 1 234 5678\\
		\Letter\ \href{mailto:X@A.ac.jp}{X\textrm{@}A.ac.jp}
	\end{minipage}
	&
	% Referee 2
	\begin{minipage}[t]{2.5in}
		Prof.\ X Y\\
		Place A\\
		Location B\\
		Country and Postcode\\
		\Telefon\ +00 1 234 5678\\
		\Letter\ \href{mailto:X@A.ac.jp}{X\textrm{@}A.ac.jp}
	\end{minipage}
\end{tabular}
\end{comment}
	%-------------------------------------------
\end{document}
